\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-10 WOOT/Files/badusb.tex
complete the coutermeasure

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. Based on this restriction several defense mechanisms were proposed  like USBCheckIn\cite{usbcheckin}\hongyi{We need more example}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually. Moreover, with video capability, our \tool achieved multiple new threat model and are tested under various scenarios.

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}
\begin{itemize}
	\item\textit{Hardware specification} the  hardware we uses to build \tool
	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
	\shuqing{Cannot bypass USBCheckIn.}
	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}

@@

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like USBCheckIn \cite{usbcheckin} is sufficient to prevent these BadUSB attack. But such defense mechanism relies on visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

>>>>

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. Based on this restriction several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}\hongyi{We need more example}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually. Moreover, with video capability, our \tool achieved multiple new threat model and are tested under various scenarios.

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}
\begin{itemize}
	\item\textit{Hardware specification} the  hardware we uses to build \tool
	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like GoodUSB\cite{tian2015defending}
	\shuqing{Cannot bypass USBCheckIn.}
	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}

@@

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism relies on visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

### 2021-01-10 WOOT/Files/experiment.tex
complete the coutermeasure

In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect Armory to the target device. 
Except performing as normal HID devices as Rubber Ducky, Armory can stream the real-time video output from the target device to the attacker through WiFi or GSM. 
Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', and upload video stream to the attacker's device.    
With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks. The attacker can control the iPad to open applications, peek at the victim's photos, etc.

@@

\yechang{Unlock status is needed or not?}

>>>>

In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect Armory to the target device. 
Except performing as normal HID devices as Rubber Ducky, Armory can stream the real-time video output from the target device to the attacker through WiFi or GSM. 
Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', a video processing utility and upload video stream to the attacker's device.    
With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks. The attacker can control the iPad to open applications, peek at the victim's photos, etc.

@@

\yechang{Unlock status is needed or not?}
\hongyi{Needed}
